% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2007-2010 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\usepackage{hyperref}
\usepackage{marvosym} % For cool symbols.

\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
            \textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\large Sruthi Petre Mallika} & \url{sruthipeter.github.io} \\
Department of Psychology, & sruthikurup@gmail.com \\ 
University of New York in Prague, &   \\
Prague, CZ.& \\
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Education}
\begin{itemize}

\item
      \ressubheading{University of New York in Prague}{Prague, Czech Republic}{Major : Psychology , GPA : 3.2}{December 2015}
      \begin{itemize}
      \resitem{Social Psychology, Psychology of Adjustment, Statistics for Social Sciences, Multivariate Statistics, Experimental Psychology, Research Methods, Psychological Measurements.}
      \end{itemize}

\end{itemize}

\resheading{Research Experience}
\begin{itemize}

    \item
        \ressubheading{Research Assistant}{Vancouver, BC}{MAGIC LAB, University of British Columbia}{Starting Jan 2017}
        \begin{itemize}
            \item{Starting a research assitantship with Prof. Kristin Laurin, focussing on goals, motivations and interpersonal structures.}
         \end{itemize}
    \item
        \ressubheading{Research Assistant}{Seattle, WA}{Stereotypes, Identity and Belonging Lab, University of Washington}{Mar - Sept 2016}
        \begin{itemize}
            \item{Assisted a post-doc with studies on academic choices and food preferences. I was responsible for programing both the studies on to \textsf{Qualtrics}, photoshopping images required for the survey, launching the study on to the UW online subject pool, running participants in lab, and entering data on to database.}
            \item{Assisted a grad student's study on Science activity. Data was collected from \textit{PAWS on Science}, a 3 day interactive science fare, using video taping. I contributed to the project by working on iMovie to retain the relevant responses of the participants during the task, by coding the videos, and by assisting with data entry.}
          \item{Assisted a former grad student's work on speeches. I helped with coding graduation speech transcriptions from the NPR database. Helped to code nearly 100 speeches.}
          \item{Volunteered to work as an RA for at least 15 hours per week. Contributed to background statistical data collection of multiple studies (using \textsf{webcaspar}), interviewed participants for studies, assisted with data entry, and data analysis (using \textsf{SPSS}).} 
         \end{itemize}
    \item
        \ressubheading{Research Assistant}{Seattle, WA}{Stereotypes, Identity and Belonging Lab, University of Washington}{Jun - Aug 2015}
        \begin{itemize}
            \item{Assisted with literature, proof reading and citation review for the meta-analysis study \textit{Why are some STEM fields more gender balanced than others? Psychological Bulletin, 42, 941-54}}
             \item{Helped with data entry and checking of multiple studies during the Summer quarter. Got the recognition to have the highest data entries of the quarter.} 
         \end{itemize}              
\end{itemize}

\resheading{Software Skills}
\begin{itemize}
\item{SPSS, R, RStudio, iMovie, Qualitrics, HTML, Markdown}
\end{itemize}


\resheading{Course Projects}
\begin{itemize}

\item
    \ressubheading{Undergraduate Thesis}{Prague, CZ}{Advisor: Prof. Judith Gerardi, SUNY Empire State College}{2015}
      \begin{itemize}
            \item{The primary research question explored whether the presence of female significant figures (eg.  female siblings) influences the power/ dominance Indian men have on their partners in romantic relationships (RR).}
            \item{The main hypothesis of the study was supported in that a higher number of female siblings enforces gender stereotypes in Indian men. Indian men with higher number of female siblings believed in higher decision power in RR. Pearson's coefficient r- value was 0.5 for the correlation between number of female siblings and decision making power index (p<0.05).}
              \item{Achieved an A- for the overall work.}
      \end{itemize}


\item
    \ressubheading{Term Papers}{Senior Year}{Notable term papers}{}
      \begin{itemize}
            \item{\textbf{Cognition (Spring 2014, Grade: A):} Submitted a term paper analysing Dr. Zenon Pylyshyn’s article ``What is cognitive science?'' in which we discussed representation- governed behavior, cognitive capacity, tri-level hypothesis of complex systems, and unconscious processing.}
            \item{\textbf{Psychology of Adolescence and Adulthood (Spring 2014, Grade: A):} Did a group project on ``Divorce'' focusing on how it affects adolescents and adults and the differences in the coping mechanisms of each group. We collected data/ statistics from the Czech Rep, UK, and US and analyzed the differences in culture, gender, effects on children, differences in the coping mechanisms of children and adults.}
            \item{\textbf{Psychology of Infancy and Adulthood (Fall 2014. Grade: A):} Detailed crtique of ``Loneliness and peer relations in young children'' by Dr. J.Cassidy and Dr. S.R.Asher. The aim of the article was to understand loneliness, determine the possibility of measuring loneliness in young children, and to test if sociometrically rejected children experience loneliness more than their peers from normal circumstances. The critique was highly appreciated.}
            \item{\textbf{Health Psychology (Spring 2014, Grade: A):} Extensive literature survey analyzing the negative influence of media on American teenages developing an eating disorder like Anorexia or Bulimia.} 
      \end{itemize}

\end{itemize}

\resheading{Volunteer Experience}
\begin{itemize}
    \item
        \ressubheading{Student Volunteer}{Prague, Czech Republic}{Pink Crocodile}{Sept 2014 - May 2015}
        \begin{itemize}
            \item{Pink Crocodile is an international non-profit organisation established in 2009 that focuses on the support of children with hearing impairment and complex needs children living under disadvantaged circumstances.} 
         \end{itemize}
    \item
        \ressubheading{Volunteer}{Prague, Czech Republic}{Charles University, 2nd Faculty of Medicine and Faculty Hospital}{Jan - Mar 2014}
        \begin{itemize}
            \item{Observation of patients who were schizophrenics, pedophiles, rapists and necrophiliacs to evaluate and study how clinical conditions and symptoms vary across different psychotic disorders.} 
         \end{itemize}

      \item
        \ressubheading{Student Assistant}{Trivandrum, India}{Valsala Nursing Home}{May - Aug 2013}
        \begin{itemize}
            \item{Assisted leading gynecologist during observation and communication with patients and participation during morning rounds.} 
         \end{itemize}                   
\end{itemize}


\resheading{References}
\begin{tabular}{lr}
% Referee 1
\begin{minipage}[t]{3.0in}
Prof.\ Sapna Cheryan \\
Associate Professor \\
Department of Psychology, Box 351525 \\
University of Washington\\
Seattle, WA 98195-1525\\
\Letter\ \href{mailto:scheryan@uw.edu}{scheryan\textrm{@}uw.edu}
\end{minipage}
&
% Referee 2
\begin{minipage}[t]{2.5in}
Prof.\ Judy Gerardi \\
Professor\\
Department of Psychology \\ 
SUNY Empire State College \\
Saratoga Springs, NY 12866 \\
\Letter\ \href{mailto:Judy.Gerardi@esc.edu}{Judy.Gerardi\textrm{@}esc.edu}
\end{minipage}
\end{tabular}

\end{document}

